High-Performance Data Analysis on Janus using Apache Spark

### 2013-12-16 paper.tex
More MapReduce stuff for introduction

In the MapReduce model, data is broken into \emph{splits} of a given size
before processing. These are stored on a distributed filesystem as
key/value pairs. The master node then distributes splits among the remaining
workers. Each of these workers runs a \emph{Map} on its split, computing for each
key/value pair $(k_1, v_1)$ another pair $(k_2, v_2)$. Each of these output
pairs is stored on the filesystem and the master is informed of their
locations.

The master node proceeds by forwarding these intermediate pairs to the
\emph{Reduce} workers, which are responsible for combining the results
for each intermediate key.

>>>>

In the MapReduce model, data is broken into \emph{splits} of a given size
before processing. These are stored on a distributed filesystem as key/value
pairs. The master node then distributes splits among the remaining workers.
Each of these workers runs a \emph{Map} on its split, computing for each
key/value pair $(k_1, v_1)$ another pair $(k_2, v_2)$. Each of these output
pairs is stored on the filesystem and the master is informed of their
locations. The master node proceeds by forwarding these intermediate pairs to the
\emph{Reduce} workers, which are responsible for combining the results for each
intermediate key.

A commonly-used example for this process is a distributed word count. First,
the input file (e.g. a large database dump containing posts on an Internet
forum) is broken into splits of a given size (say 64MB). The splits store
$(k, v)$ pairs such that each $v$ is a record (a post). The \emph{Map} task
is responsible for mapping each record to a set of (word, count) pairs,
which are written to the filesystem.

The next step is for a \emph{Reduce} worker to sort these records by key
and then sum together the values for each given key, and write out
a set of (word, count) records where the keys are now unique.

This simple example has interesting implications for MapReduce in general.
We can see that \emph{Map} tasks are highly-parallel, but \emph{Reduce}
introduces a serial bottleneck. In cases like parallel word count, where the
\emph{Reduce} is associative and commutative (i.e. forms a commutative
semigroup over the set of values), there is an additional opportunity for
parallelism. As such, MapReduce provides an additional task, called a
\emph{Combiner}, which assumes this structure and can be used to distill
the intermediate $(k, v)$ pairs before a \emph{Reduce}.
